We are interested in the relationship between the following variables:
Y = X.Donated.From.Big.Oil
X = NUCLEAR, COAL, NATURAL.GAS, PETROLEUM, HYDRO, GEOTHERMAL, SOLAR, WIND, and BIOMASS

Particularly with Coal, because that is predominantly what is being lobbied for by the "Big Oil" companies in this data.

Hypothesis:
H0: There is a negative relationship between X.Donated.From.Big.Oil and Coal.
H1: There is a positive relationship between X.Donated.From.Big.Oil and Coal.

```{r echo=F, message=F}
# PDF Config
pdf("Multiple Linear Regression.pdf", width = 8.5, height = 9)

# Libraries
library(corrplot)

# Import Data
data <- read.csv("US_General.csv", header = TRUE, sep = ",")

# Rename Y to be less politically charged
Oil.Lobbying <- data$X.Donated.From.Big.Oil

# Adjust Y for Population and GDP
Y <- cbind(Oil.Lobbying,
           Oil.Lobbying / data$Population,
           Oil.Lobbying / data$State.GDP.Q4.2021,
           Oil.Lobbying / (data$State.GDP.Q4.2021 / data$Population))

# Add names to Y for readability
ynames <- cbind("Oil Lobbying", "Oil Lobbying / Population", "Oil Lobbying / State GDP", "Oil Lobbying / State.GDP.Q4.2021 / Population")
```

```{r echo=F}
# For loop to iterate through each Y for Multiple Linear Regression, Correlation Matrix, and Scatterplots
# define function
main <- function(Y, ynames) {
data <- data.frame(Y, data$NUCLEAR, data$COAL, data$NATURAL.GAS, data$PETROLEUM, data$HYDRO, data$GEOTHERMAL, data$SOLAR, data$WIND, data$BIOMASS)

# Rename the Columns to be more readable
names(data) <- c("Y", "NUCLEAR", "COAL", "NATURAL.GAS", "PETROLEUM", "HYDRO", "GEOTHERMAL", "SOLAR", "WIND", "BIOMASS")

# Perform Multiple Linear Regression
# Significance Levels = 0.01, 0.05, 0.1
model <- lm(Y ~ ., data = data)

# Print the Model Summary and name of Y
print(paste("Y=", ynames))

print(summary(model))

# Correlation Matrix
cor <- cor(data)

# Output the Correlation Matrix with red and green colors

# Method = Circle
corrplot(cor,
         method = "circle",
         col = c("red", "green"),
         mar = c(0, 0, 2, 0),
         title = paste("Y=", ynames))

# Method = Number
corrplot(cor,
         method = "number",
         col = c("red", "green"),
         mar = c(0, 0, 2, 0),
         title = paste("Y=", ynames))

# For loop to make a scatterplot for each X variable
for (j in 2:ncol(data)) {

# Output Scatterplot
plot(data[, j],
     data[, 1],
     xlab = names(data)[j],
     ylab = names(data)[1],
     main = paste(names(data)[1], "vs", names(data)[j]))

# Output Regression Line with Scatterplots
abline(lm(data[, 1] ~ data[, j]), col = "red")
}
}
```

```{r echo=F}
# Print warnings, if any
warnings()
```

```{r echo=F, message=F}
main(Y[, 1], ynames[, 1])
```

```{r echo=F, message=F}
main(Y[, 2], ynames[, 2])
```

```{r echo=F, message=F}
main(Y[, 3], ynames[, 3])
```

```{r echo=F, message=F}
main(Y[, 4], ynames[, 4])
```
